 

### 2023-02-22 thesis.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

---
title: " "		
output:
  pdf_document:
    number_sections: TRUE
    # citation_package: natbib

@@

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}
  # - \usepackage{float}
  # - \usepackage{chapterbib}
  # - \usepackage{lastpage}
  # - \usepackage{dcolumn}
  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
  # - \addbibresource{bibliography.bib}

@@

@@

```{r setup0, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE)

@@

Imperdiet sed euismod nisi porta lorem mollis aliquam. Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim. Eget lorem dolor sed viverra. Vitae proin sagittis nisl rhoncus mattis. Mi sit amet mauris commodo quis imperdiet massa tincidunt. Quis auctor elit sed vulputate mi. Augue eget arcu dictum varius duis at consectetur lorem. Commodo elit at imperdiet dui accumsan sit amet. Consequat semper viverra nam libero justo laoreet sit. Quis hendrerit dolor magna eget est lorem ipsum. Eget arcu dictum varius duis at consectetur lorem. Fermentum posuere urna nec tincidunt praesent semper feugiat. Integer quis auctor elit sed vulputate mi sit amet. Ultricies integer quis auctor elit. Metus vulputate eu scelerisque felis imperdiet proin fermentum. Ut porttitor leo a diam sollicitudin tempor id eu nisl. Cras adipiscing enim eu turpis egestas. Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.

@@

@@

# Separate bibliography for each section
# Numbered figures and tables by section
# Check that sequential articles are represented by a dash
# Table of figures and tables
# Acronyms with acronym down
# Institutional authors need to be fixed in bibliography

>>>>

---
title: " "		
output:
  pdf_document:
    pandoc_args: !expr acronymsdown::add_filter()
    number_sections: TRUE
    # citation_package: natbib

@@

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}
  # - \usepackage{acro}
  # - \usepackage{float}
  # - \usepackage{chapterbib}
  # - \usepackage{lastpage}
  # - \usepackage{dcolumn}
  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
  # - \addbibresource{bibliography.bib}

@@

acronyms:
  insert_loa: false
  loa_title: ""

  # loa_title: "List of Acronyms"
  keys:
    - shortname: LMIC
      longname: low and middle income country

@@

```{r setup0, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE) 
library(acronymsdown)
```

@@

Imperdiet sed euismod nisi porta lorem mollis aliquam. Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim. Eget lorem dolor sed viverra. Vitae proin sagittis nisl rhoncus mattis. Mi sit amet mauris commodo quis imperdiet massa tincidunt. Quis auctor elit sed vulputate mi. Augue eget arcu dictum varius duis at consectetur lorem. Commodo elit at imperdiet dui accumsan sit amet. Consequat semper viverra nam libero justo laoreet sit. Quis hendrerit dolor magna eget est lorem ipsum. Eget arcu dictum varius duis at consectetur lorem. Fermentum posuere urna nec tincidunt praesent semper feugiat. Integer quis auctor elit sed vulputate mi sit amet. Ultricies integer quis auctor elit. Metus vulputate eu scelerisque felis imperdiet proin fermentum. Ut porttitor leo a diam sollicitudin tempor id eu nisl. Cras adipiscing enim eu turpis egestas. Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.[@vaidyanathanEvaluationInternetSearches2022]

This is a \acr{LMIC}. This is also a \acr{LMIC}.

@@

\section*{References}

\addcontentsline{toc}{section}{References}

<div id="refs"></div>

\section*{Supplementary materials}

\addcontentsline{toc}{section}{Supplementary materials}

```{r appendix_all, child='appendix.Rmd'}
```

@@

# Maps in Chapter 1 need to be improved to eliminate errors in cartographic resolution
# Separate bibliography for each section
# Numbered figures and tables by section
# Check that sequential articles are represented by a dash
# Table of figures and tables
# Acronyms with acronym down
# Institutional authors need to be fixed in bibliography
